---
title: "Project 2"
author: "GP SINGH"
date: "March 8, 2016"
output: html_document
---
```{r}
library(tidyr)

library(dplyr)

library(stringr)

library(RCurl)
```


## DataSet 1


The dataset consists of number of applications received for firearms transfers, the rejections and rate of felonies from 1999 - 2010.

```{r}
# reading the data and skipping first 12 lines for data cleaning
firearms<- read.csv("https://raw.githubusercontent.com/gpsingh12/IS-607-MSDA/master/background_check.csv", skip=12, stringsAsFactors = TRUE)
head(firearms)


# rename the columns of the dataset
names(firearms) = c("Year", "Applications", "Rejected", "pct_rejected","X.1", "felonies", "pct_felonies", "X.2", "Rate")

# the formatting of the csv file has additional empty columns, we will remove those columns
firearms <- firearms[, -5]
firearms <- firearms[, -7]

#removing the first row of the data set 
firearms <- firearms[-c(1),]
head(firearms)
# the column Rejected has vales that need to be converted into numeric values by removing unneccessary signs (",")
rejection<-as.numeric(sub("\\,","", firearms$Rejected)) 

rate<- firearms$Rate


#Creating a data frame for Analysis
data = data.frame(firearms$Year, firearms$Applications, rejection, firearms$pct_rejected, firearms$felonies, firearms$pct_felonies, rate)
data
```



### Analysis

Rate of felonies per 1000 applications depends on number of applications rejected each year.  Is there any correlation between two variables.

(or Can a linear model be created to predict one varible using other)

we need to find relation between rate and rejection. i.e whetehr one is predictor of the other variable. The most common and effective way is checking for correlation between these two variables to check whether it is appropriate to create a linear regression model or not. 
```{r}
cor(data$rejection,data$rate)
```

strong correlation between these two variables.
We will check this further by creating a scatter plot and checking if it is a straight line
```{r}
plot(rate, rejection)
```   


Althoughthe scatterplot does not predict any strong correlation, yet we will proceed with the regression model

```{r}
model1<- lm(formula = rejection ~ rate  , data = data)
summary(model1)
# model 
# rejection = 101667 + 5301* rate
```



## DataSet 2




Dataset consists of oil consumption details of various brands in the first half of 2015 along with the opening balances.


```{r}

# reading the data

oil<- read.csv("https://raw.githubusercontent.com/gpsingh12/IS-607-MSDA/master/oil_data.csv", na.strings=FALSE, skip = 2)

oil

# name the missing headers

oil[2,1]<-c("Open")
oil[4,1]<-c("Jan")
oil[6,1]<-c("Feb")
oil[8,1]<-c("Mar")
oil[10,1]<-c("Apr")
oil[12,1]<-c("May")
oil[14,1]<-c("Jun")


#Extracting the data and converting to numeric

a<-(sub("\\:", "", oil$Caltex))
b<-(sub("\\:", "", oil$Gulf))
c<- (sub("\\:", "", oil$Mobil))

x<-as.numeric(unlist(str_extract_all(a,"[:digit:]{2,}")))
y<-as.numeric(unlist(str_extract_all(b,"[:digit:]{2,}")))
z<-as.numeric(unlist(str_extract_all(c,"[:digit:]{2,}")))

# from brand name we swlect alternate values for purchase and consumption after #extracting them
Caltex_pur <-x[c(1,3,5,7,9,11,13,15,17,19,21,23,25,27)]
Caltex_cons <-x[c(2,4,6,8,10,12,14,16,18,20,22,24,26,28)]

Gulf_pur<- y[c(1,3,5,7,9,11,13,15,17,19,21,23,25,27)]
Gulf_cons<-y[c(2,4,6,8,10,12,14,16,18,20,22,24,26,28)]


Mobil_pur<-z[c(1,3,5,7,9,11,13,15,17,19,21,23,25,27)]
Mobil_cons<-z[c(2,4,6,8,10,12,14,16,18,20,22,24,26,28)]

oil_data <-data.frame(oil$Month, oil$Category, Caltex_pur,Caltex_cons,Gulf_pur,Gulf_cons,Mobil_pur,Mobil_cons)
oil_data
```



###Analysis
```{r}
#closing balance of  brand

oil_data1 =oil_data%>%
  mutate(Caltex_Close= Caltex_pur - Caltex_cons)
oil_data2 = oil_data1 %>%
  mutate(Gulf_Close = Gulf_pur - Gulf_cons)

oil_data3 = oil_data2 %>%
  mutate(Mobil_Close = Mobil_pur-Mobil_cons)
oil_data3

#Closing balance of three brands
closing_bal_Caltex<- sum(oil_data3$Caltex_Close)
closing_bal_Gulf<- sum(oil_data3$Gulf_Close)
closing_bal_Mobil<- sum(oil_data3$Mobil_Close)

closing_bal_Caltex
closing_bal_Gulf
closing_bal_Mobil

#closing balance of components

Eng_Oil<- subset(oil_data3, oil_data3$oil.Category == "Engine Oil")
Gear_Oil<- subset(oil_data3, oil_data3$oil.Category == "GearBox Oil")
Eng_Oil
Gear_Oil

#closing balance of Engine oil

cbal1<- sum(Eng_Oil$Caltex_Close) + sum(Eng_Oil$Gulf_Close)+
                sum(Eng_Oil$Mobil_Close)
cbal1


#closing balance of Gearbox oil

cbal2<-sum(Gear_Oil$Caltex_Close) + sum(Gear_Oil$Gulf_Close)+
                sum(Gear_Oil$Mobil_Close)
cbal2



# Most consumed brand across two categories of oil

oil_data3

cal<- as.numeric(max(oil_data3$Caltex_cons))
gulf<-max(oil_data3$Gulf_cons)
mobil<-max(oil_data3$Mobil_cons)
cal
gulf
mobil

```


Caltex is the most consumed brand across two categories of oil

## Dataset 3

Find the total percent difference from the estimates (high and low) and the sold prices. (Sold Price - High Estimate)/High Estimate = % -- There should be two answers: High Difference and Low Difference

```{r}
# reading the data
auction <- read.csv("https://raw.githubusercontent.com/gpsingh12/IS-607-MSDA/master/auction.csv")

#removing unwanted columns in csv file
auction <- auction[ , c(-2)]
auction

#extracting the data 
x<-(sub("\\-", "", auction$Range)) 
x
y<-(sub("\\$", "", auction$Price))
df <- c(auction$Lot, x,y)
Price <- as.numeric(y)
Year<-as.numeric(auction$Lot)


b1<- sub("\\$", "", x)
b2<-sub("  \\$", " ", b1)

b3<-unlist(str_extract_all(b2," [:digit:]{3}"))
hrange<-as.numeric(b3)
b4<-unlist(str_extract_all(b2, "[:digit:]{2,}"))

b5<- b4[c(1,3,5)]
lrange<- as.numeric(b5)
# creating the data frame

auc <- data.frame(Year, lrange,hrange,Price)

auc

```

###Analysis


Find the total percent difference from the estimates (high and low) and the sold prices. (Sold Price - High Estimate)/High Estimate = %


```{r}

# adding another columns as required in Analysis

auct = auc%>%
  mutate(`High Difference` = ((Price-hrange)/hrange)*100)
auc1 = auct%>%
  mutate(`Low Difference`= ((Price-lrange)/lrange)*100)
auc1
```

