---
title: "Project 1"
author: "GP SINGH"
date: "February 23, 2016"
output: html_document
---



```{r}
library(RCurl)
library(stringr)


chess_data <- read.csv("https://raw.githubusercontent.com/gpsingh12/IS-607-MSDA/master/tournament.txt", header = TRUE, skip=2)
#using skip=2 will remove first three lines as USCF and ID were adding up to the substrings created
head(chess_data)

cd<-unlist(chess_data)

```



The data given in the original format needs to be separated and stored as different variables, which can be combined later on to create the output as csv file.


We will start with unlisting players names.


Create a variable player containing names of the players.

```{r}
player <- str_trim(unlist(str_extract_all(cd, "([[:alpha:]., ]-?){7,}")))
head(player)
```



State represent the names of the states of the players by extracting the information from text file.

```{r}
state <- str_trim(unlist(str_extract_all(cd, "\\  [[:upper:]]{2}")))
head(state)
```



 Extract the player scores.
 
```{r}
scores<-str_trim(unlist(str_extract_all(cd, "[0-9]\\.[0-9]-?")))
head(scores)
```



Ratings of the players

```{r}
rating<-unlist(str_extract_all(cd, "\\: [[:digit:] ]{4}"))

head(rating)

rating_upd <- sub(pattern = ': ', replacement = '', rating)


prerating<- as.numeric(rating_upd)
head(prerating)
```



Opponents pre ratings


```{r}
oppavg=unlist(str_extract_all(cd, "\\|[[:upper:]]  [[:digit:] ]{1,}"))

head(oppavg)



oavg <- as.numeric(unlist(str_extract_all(oppavg,"[[:digit:]]{1,2}")))
head(oavg)


# using python's ideology , finding the number in a list using index, I will create a vector opponent. i.e using a number from oavg it will retrieve the score corresponding to the prerating.
opponent<- (prerating[oavg])
head(opponent)
 # once we have the list of scores of opponents, we will create a matrix to perform mathematical operations (mean).

avg_opp <- matrix(opponent,7,64)




# take the transpose of the matrix to convert it into a matrix of 64 x 7 as required 
#in accordance with the text file.
opp1<-t(avg_opp)
head(opp1)
# we have a matrix of 64 rows and 7 columns where a11 (first element of row1 and column 1 represent the pre rating of the player 39. Similarly a12 represent element at position row1 and column2 i.e it corresponds to the rating of player 21 (1563) and so on.)
 
opp_prerating <- rowMeans(opp1, n=7)
opp_prerating<- as.integer(opp_prerating)
opp_prerating<- round(opp_prerating, digits=4)
head(opp_prerating)

```





```{r}

chess <- data.frame(player, state, scores, prerating, opp_prerating)

head(chess)


write.csv(chess, "C:/Users/Gurpreet/Documents/IS607/chessdata.csv")
```

