---
title: "Spam/Ham"
author: "GP SINGH"
date: "April 4, 2016"
output: html_document
---


###It can be useful to be able to classify new "test" documents using already classified "training" documents.  A common example is using a corpus of labeled spam and ham (non-spam) e-mails to predict whether or not a new document is spam.  

For this project, you can start with a spam/ham dataset, then predict the class of new documents (either withheld from the training dataset or from another source such as your own spam folder).


#### Installing required packages and libraries


```{r}
library(kernlab)
library(knitr)
library(rpart)
library(e1071)
library(RTextTools)
library(randomForest)
library(ROCR)

```

###**Data Collection**

The dataset is retrieved form UCI Machine Learning Repository. Information about the dataset can be accessed using the [link](https://archive.ics.uci.edu/ml/machine-learning-databases/spambase/)

We will use two different approaches for reading the data in r.

#### ***Approach: 1***


We will install the package kernlab. The library(kernlab) contain the dataset which can be used with ease for
creating models for spam detection.

we will use r command data(spam) to get the data in r.

```{r}
data(spam)

kable(head(spam))

dim(spam)


```


 The second approach is copying and saving the data in csv file and reading it in r. There is another file `name_data` which contains the names of the variables.After reading it in r, the two files data and `name_data` are  merged using a function, where `name_data` is appended to the header row of data.
####***Approach 2***

```{r}

dataset <- read.csv("data.csv",header=FALSE,sep=";")
names <- read.csv("name_data.csv",header=FALSE,sep=";")
names(dataset) <- sapply((1:nrow(names)),function(i) toString(names[i,1]))

kable(head(dataset))
```


The two approaches used provide same datasets. 


####**Splitting the data into training and test data sets**

Once we have the data for spam emails, we will split that dataset into training and test datasets. We will select 80% of the data randomly from our dataset to test it against the remaining 20% test dataset.

```{r}
sub <- sample(nrow(spam), floor(nrow(spam) * 0.8))
train <- spam[sub, ]
test <- spam[-sub, ]



dim(train)
dim(test)
```


The training and test datasets are now used for creating the models.




###***SVM model***

```{r}
svm.model <- svm(type~., data = train)


svm.pred <- predict(svm.model,test[1:57,])

svm.pred <- predict(svm.model,test)


tab <-table(predicted = svm.pred, actual = test[,58])


# to find the precision and accuracy we can use caret library. I was having problems even after the caret libraryy was installed. I used a manual technique for calculating the accuracy of the models

#TP = True Positive
#TN = True Negative
#FP = False Positive
#FN = False Negative

TP <-tab[2,2]
TN <-tab[1,1]

FP<-tab[1,2]
FN<-tab[2,1]

Accuracy_SVM<- (TN + TP)/(TN+TP+FN+FP)
Accuracy_SVM

```




###***Recursive Partitioning***



```{r}


rpart.model <- rpart(type~., data =train)
rpart.pred <- predict(rpart.model,test, type = "class")
tab <-table(predicted=rpart.pred,actual=test[,58])
TP <-tab[2,2]
TN <-tab[1,1]

FP<-tab[1,2]
FN<-tab[2,1]

Accuracy_RecPart<- (TN + TP)/(TN+TP+FN+FP)
Accuracy_RecPart
```

###***Random Forest***

```{r}


spam.rf<-randomForest(type~.,data=train)
rf.pred <- predict(spam.rf, test)
tab <-table(predicted=rf.pred,actual=test[,58])

tab
TP <-tab[2,2]
TN <-tab[1,1]

FP<-tab[1,2]
FN<-tab[2,1]

Accuracy_RF<- (TN + TP)/(TN+TP+FN+FP)
Accuracy_RF
```



Comparing the accuracies of three models

```{r}

Accuracy <- data.frame(Accuracy_SVM, Accuracy_RecPart, Accuracy_RF)

kable(Accuracy)
```



#### Random Forest has better accuracy followed by SVM and Recursive Partitioning.

#### Reference:


http://www.gettinggeneticsdone.com/2011/02/split-data-frame-into-testing-and.html

https://en.wikibooks.org/wiki/Data_Mining_Algorithms_In_R/Classification/SVM


https://www.researchgate.net/post/Whats_the_difference_between_training_set_and_test_set