---
title: "Assignment  10"
author: "GP SINGH"
date: "March 30, 2016"
output: html_document
---


The New York Times web site provides a rich set of APIs, as described here:
http://developer.nytimes.com/docs
You'll need to start by signing up for an API key.
Your task is to choose one of the New York Times APIs, construct an interface in R to read in the JSON data, and transform it to an R dataframe.


####**Required libraries**

```{r}
library(jsonlite)
library(knitr)


```



####**Registering for an API key**

To request for NY Times API key, register at  [link](https://myaccount.nytimes.com/register)



The information about creating query and url to be used can be found [here](http://developer.nytimes.com/docs/read/article_search_api_v2#h2-requests)



Web API and URL
```{r}

api_key <- "&api-key=e2ecd4b8ba0d275c1ae6a42a808a991e:5:74859716"

url <- "http://api.nytimes.com/svc/search/v2/articlesearch.json?q=Clinton-Trump"

# the query Clinton-Trump was used by me. We can choose different terms and further refine the queries 
```


####**Reading the json data in r and converting it into a data frame**

```{r}
dat <- (paste0(url, api_key))

dat <-fromJSON(dat)


#converting dat into a dataframe
df <- as.data.frame(dat$response)
names(df)


# creating data frame for the required terms

dataframe <- data.frame(df$docs.section_name,df$docs.lead_paragraph, df$docs.abstract, df$docs.web_url)


kable(dataframe)
```

